A Set-based Algorithm for Computing Strongly Connected Components of a Graph

### 2022-08-16 Isabelle/document/root.tex
refactored proofs and explanations

\title{Correctness of an algorithm for computing strongly connected components of a graph}
\author{Stephan Merz and Vincent Trélat}
\maketitle

@@

% optional bibliography
%\bibliographystyle{abbrv}
%\bibliography{root}

>>>>

\title{A Set-based Algorithm for Computing Strongly Connected Components of a Graph}
\author{Stephan Merz and Vincent Trélat}
\maketitle

\begin{abstract}
  We prove the correctness of a sequential algorithm for computing strongly
  connected components (SCCs) of a graph due to Vincent Bloemen.
\end{abstract}

@@

% optional bibliography ... doesn't appear to work
%\bibliographystyle{abbrv}
%\bibliography{root}

\begin{thebibliography}{9}
\bibitem{bloemen:strong}
Vincent Bloemen.
\newblock Strong Connectivity and Shortest Paths for Checking Models.
\newblock University of Twente, Enschede, The Netherlands, 2019.
  \url{https://ris.utwente.nl/ws/portalfiles/portal/122499728/thesis.pdf}

\bibitem{dijkstra:finding}
Edsger W. Dijkstra.
\newblock Finding the Maximum Strong Components in a Directed Graph.
\newblock In: Selected Writings in Computing -- A Personal Perspective,
  pp.\ 22-30.
  Texts and Monographs in Computer Science. Springer, 1982.

\bibitem{munro:efficient}
J. Ian Munro.
\newblock Efficient Determination of the Transitive Closure of a Directed Graph.
\newblock \emph{Information Processing Letters} 1(2):56-58, 1971.

\bibitem{tarjan:depth-first}
Robert Tarjan.
\newblock Depth first search and linear graph algorithms.
\newblock \emph{SIAM Journal on Computing}, 1972.
\end{thebibliography}
